---
title: "My First Report"
author: "Yvonne"
format:
  html:
    embed-resources: true
---

## Welcome to your practice report

This is a **Quarto** document. It mixes ordinary writing with live code, so your
report and your analysis always stay in sync. When you click **Render**, Quarto
runs the code below and builds a finished HTML page.

Try it now: change `author: "Your Name"` in the header above to your own name,
then click **Render**.

## A first look at the data

The code chunk below reads a small practice dataset from the `data/` folder and
shows the first few rows.

```{r}
patients <- read.csv("data/patients.csv")
head(patients)
```

## A first chart

```{r}
hist(patients$age,
     main = "Age distribution of practice patients",
     xlab = "Age (years)",
     col  = "steelblue")
```

## Your turn

- Add a sentence here describing what you notice in the chart.
- Render again and check that both your sentence and the chart appear.

When you are happy with the result, **commit and sync** your work (the Week 2
course page walks you through this), then submit your repository link on Canvas.

## My Notes

- What I  learned today in class: I know new code language used in codespaces. The **2 `**` means bold the text i want**, and the 3 "`" with {} means build a code out of text. I also learned the quorto render the document to a new fromat. I need to remember committed what I chaged to the original document and push the changes to the folder.
The easiest part is that render the document by following all proser doing in class. But because my computer uses different language, the instruction on my GitHub pages looks a little bit different and I need to remember the English of the botton I click to on my computer.

```{r}
summary(patients)
```